Estimating duration in the presence of misclassification

### 2024-02-08 cis-imperfect-testing.tex

The incorporation of false negatives into survival analysis is an area of much interest, especially in the application of tests for HIV infants~\autocite[e.g.]{brownBayesian,balasubramanianEstimation}.
\Textcite{piresIntervalMisclassify} provide a comprehensive review of approaches.
However, false negatives with either doubly censored or truncated data has not been addressed.
The situation here requires both.

>>>>

The inclusion of false negatives into survival analysis is an area of much interest, especially in the application of tests for HIV in infants~\autocite[e.g.][]{brownBayesian,balasubramanianEstimation};
\textcite{piresIntervalMisclassify} provide a comprehensive review of approaches.
However, including false negatives with either doubly censored or truncated data has not been addressed.
The situation here requires both.
